### 2018-07-06 paper/6-engineering.tex
Expand the Frankenbuild explanation

\begin{figure}
\vspace{-2mm}
\begin{subfigure}[b]{0.25\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-build.pdf}}
\vspace{-1mm}
\caption{Initial build}
\end{subfigure}
\begin{subfigure}[b]{0.40\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-clean.pdf}}
\vspace{-1mm}
\caption{Clean up and evict \cmd{main.prof}}
\end{subfigure}
\begin{subfigure}[b]{0.31\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-rebuild.pdf}}
\vspace{-1mm}
\caption{Build \cmd{main.prof} and \cmd{report.txt}}
\end{subfigure}
\caption{A Frankenbuild example: (a)~build a human-readable profiling report for
\cmd{main.exe} from information dump \cmd{main.prof} produced by a profiling
tool and record deep constructive traces in the cloud, (b)~remove built files
locally and evict \cmd{main.prof} from the cloud storage, (c)~build
\cmd{main.prof} by executing the profiler (profiling is non-deterministic, hence
the new hash), then build \cmd{report.txt} by downloading it from the matching
deep constructive trace in the cloud, resulting in a Frankenbuild because
\cmd{main.prof} and \cmd{report.txt} are inconsistent. New and evicted cloud
storage entries are highlighted; file hashes are shown in circles.
\label{fig-frankenbuild}}
\vspace{-3mm}
\end{figure}

Deep constructive traces (\S\ref{sec-deep-constructive-traces}) combined with
task non-determinism (\S\ref{sec-non-determinism}) can lead to very subtle bugs,
especially in the cloud setting. Fig.~\ref{fig-frankenbuild} shows a
\emph{Frankenbuild}~\cite{esfahani2016cloudbuild} example, where the target
\cmd{report.txt}, which is downloaded from the cloud, is inconsistent with its
immediate dependency \cmd{main.prof}. This is caused by (i)~inherent
non-determinism of profiling: running a profiling tool on the very same
\cmd{main.exe} will produce different \cmd{main.prof} results every time; and
(ii)~relying on deep constructive traces, which cache build results based only
on the hashes of terminal task inputs.

>>>>

\begin{figure}
\vspace{-2mm}
\begin{subfigure}[b]{0.25\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-build.pdf}}
\vspace{-1mm}
\caption{Initial build}
\end{subfigure}
\begin{subfigure}[b]{0.40\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-clean.pdf}}
\vspace{-1mm}
\caption{Clean up and evict \cmd{main.prof}}
\end{subfigure}
\begin{subfigure}[b]{0.31\linewidth}
\centerline{\includegraphics[scale=0.28]{fig/frankenbuild-example-rebuild.pdf}}
\vspace{-1mm}
\caption{Build \cmd{main.prof} and \cmd{report.txt}}
\end{subfigure}
\vspace{-1mm}
\caption{A Frankenbuild example: (a)~build a human-readable profiling report for
\cmd{main.exe} from information dump \cmd{main.prof} produced by a profiling
tool and record deep constructive traces in the cloud, (b)~remove built files
locally and evict \cmd{main.prof} from the cloud storage, (c)~build
\cmd{main.prof} by executing the profiler (profiling is non-deterministic, hence
the new hash), then build \cmd{report.txt} by downloading it from the matching
deep constructive trace in the cloud, resulting in a Frankenbuild because
\cmd{main.prof} and \cmd{report.txt} are inconsistent. New and evicted cloud
storage entries are highlighted; file hashes are shown in circles.
\label{fig-frankenbuild}}
\vspace{-4mm}
\end{figure}

Deep constructive traces (\S\ref{sec-deep-constructive-traces}) combined with
task non-determinism (\S\ref{sec-non-determinism}) can lead to very subtle bugs,
especially in the cloud setting. Fig.~\ref{fig-frankenbuild} shows a
\emph{Frankenbuild}~\cite{esfahani2016cloudbuild} example, where the target
\cmd{report.txt}, which is downloaded from the cloud, is inconsistent with its
immediate dependency \cmd{main.prof}. This is caused by two factors:
(i)~inherent non-determinism of profiling: running a profiling tool on the very
same \cmd{main.exe} will produce different \cmd{main.prof} results every time;
and (ii)~relying on deep constructive traces, which cache build results based
only on the hashes of terminal task inputs (in this case \cmd{main.exe}). Note
that the resulting store is incorrect according to all three definitions of
correctness: the main definition (\S\ref{sec-build-correctness}), the variant
for non-deterministic tasks (\S\ref{sec-non-determinism}) and the variant for
shallow builds (this section).
